Equalizer\\Programming and User Guide

### 2009-12-23 Developer/ProgrammingGuide/paper.tex
CUDA section added, including hint_cuda_GL_interop. More to come...

Written by Stefan Eilemann.\\
Engineering contributions by Maxim Makhinya, Jonas B\"osch, Christian
Marten, Sarah Amsellem and Patrick Bouchaud.

@@

@@

@@

{\footnotesize\begin{lstlisting}
pipe
{
    name     string
    port     unsigned     # X server number or ignored
    device   unsigned     # graphics adapter number
    viewport [ viewport ] # default: autodetect
    attributes
    {
        hint_thread   OFF | ON   # default ON
    }

>>>>

Written by Stefan Eilemann.\\
Engineering contributions by Maxim Makhinya, Jonas B\"osch, Christian
Marten, Sarah Amsellem, Patrick Bouchaud and Philippe Robert.

@@

\subsection{\label{sCUDA}GPU Computing with CUDA}

The Equalizer parallel rendering framework can be used to scale GPU 
computing applications (also known as GPGPU) based on CUDA. The necessary
steps to write a distributed GPGPU application using Equalizer are described
in the following.

Please note that the support for CUDA is only enabled if the CUDA libraries are found
in their default locations. Otherwise please adapt the makefiles accordingly.

\subsubsection{CUDA Initialization}

Equalizer automatically initializes a CUDA context on each pipe (using the specified
device number) whenever \textsf{hint\_cuda\_GL\_interop} is set. The initialization is 
currently done using the CUDA runtime API in order to support device emulation. 
On the other side, if this hint is not set the OpenGL interop feature is not enabled, and 
furthermore, the GPU which executes CUDA code defaults to device 0.

Once CUDA is initialized correctly, C for CUDA can be used as any other GPU 
programming interface.

\subsubsection{CUDA Memory Management}

Equalizer does not provide any facility to perform memory transfer from and to the CUDA
devices. This is entirely left to the programmer.

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_PIPE\_IATTR\_HINT\_CUDA\_GL\_INTEROP\\
  \textbf{Value} & OFF \textbar \ ON\\
  \textbf{Default} & OFF\\
  \textbf{Details} & Determines if the pipe thread enables interoperability between CUDA
  and OpenGL or not. When set to ON, the CUDA device is configured on which the 
  thread executes the CUDA device code. If no graphics adapter is specified in the config 
  file, the one providing the highest compute performances on the particular node is chosen. 
  When set to OFF, no CUDA device is configured at all.\\
  \hline
\end{tabularx}\\\vfill

@@

{\footnotesize\begin{lstlisting}
pipe
{
    name     string
    port     unsigned     # X server number or ignored
    device   unsigned     # graphics adapter number
    viewport [ viewport ] # default: autodetect
    attributes
    {
        hint_thread            OFF | ON   # default ON
        hint_cuda_GL_interop   OFF | ON   # default OFF
    }
